---
title: "Map issue"
author: "Kieran healy"
date: "11/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(ggplot2)
library(maptools)
library(mapproj)
library(rgeos)


library(rgdal)
library(gdalUtils)

library(scales)

theme_set(theme_minimal())

```


## An Albers projection string
```{r}
aea_proj  <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23
+lon_0=-96 +datum=WGS84 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"

```


## Data

### Book / County data

US County data as per Bob Rudis and the book

```{r}
ogrInfo("us_counties/gz_2010_us_050_00_5m.json")
county_raw <- readOGR(dsn="us_counties/gz_2010_us_050_00_5m.json")
```

### 2017 TIGER/Line state shapefiles from Minnesota Pop Center

```{r}
ogrListLayers("min_pop")

state_raw <- readOGR(dsn = "min_pop", layer = "US_state_2017")

```


# The map sizes are different

This messes up the manual transformation.

## Counties

```{r}
county_aea <- spTransform(county_raw, aea_proj)

raster::crs(county_aea)
raster::extent(county_aea)
bbox(county_aea)
```

## County Plot

```{r}
p <- ggplot(data = county_aea, 
            mapping = aes(x=long, y=lat, group=group))

p + geom_polygon(color="gray80",
                   size=0.2) + 
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(labels = scales::comma,
                       breaks = c(-7e6, -6e6, -4e6, -2e6,
                                  0, 2e6, 3e6))

```

## States

```{r}
state_aea <- spTransform(state_raw, aea_proj)

## Simplify polygons---otherwise it's huge
## This will take a little while
state_aea_sim <- rmapshaper::ms_simplify(state_aea, keep = 0.01)

raster::crs(state_aea_sim)
raster::extent(state_aea_sim)
bbox(state_aea_sim)
```

Notice now `xmin` differs by a lot. I think this is what's messing things up when we slice out Alaska and Hawaii. The boxes defining those areas are larger in the State map, including more ocean/white space, and this botches the insertion into the lower 48 map.

## State Plot

```{r}
p <- ggplot(data=state_aea_sim,
            aes(x=long, y=lat, group=group)) 

p + geom_polygon(color="gray80",
                   size=0.2) + 
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(labels = scales::comma,
                       breaks = c(-7e6, -6e6, -4e6, -2e6,
                                  0, 2e6, 3e6))

```



